Awareness and Experience of Developers to\\ Outdated and License-violating Code on Stack Overflow:\\ The Online Survey

### 2017-10-19 cloverflow_technical_report/cloverflow_survey_rn.tex
Completed the whole paper (RQ1 - RQ5).
Updated the number of Group 2 in technical report due to removing one participant.

\subsubsection{The visitor survey} 
The survey consists of 16 questions: 9 Likert's
scale questions, 3 yes/no questions, 2 multiple-choice questions, and 2
open-ended questions. The first four questions are mandatory while the other 12
questions will be shown to the participants based on their previous answers. The
survey collects information about the participant's software development
experience, the importance of Stack Overflow, reasons for reusing Stack Overflow
snippets, problems from Stack Overflow snippets, licensing of code on Stack
Overflow, and additional feedbacks. The survey was open for participation for 50
days, from 25 July 2017 to 12 September 2017, before we collected and analysed
the responses.

@@

\begin{table}
	\centering
	\caption{The Stack Overflow answerer taken the surveys}
	\label{tab:answerers}
	\begin{tabular}{lrrrr}
		\toprule
		Target group & Reputation & Sent emails & Answers & Rate \\
		\midrule
		Answerer Group 1 & 963,731--7,674 & 300 & 117 & 39\% \\
		Answerer Group 2 & 7,636--6,999 & 307 & 85 & 28\% \\
		\midrule
		Total & -- & 607 & 202 & 33\% \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\subsection{The answerer survey}
We received 117 answers (39\% response rate) from the first group and 85 answers
(28\% response rate) from the second group of Stack Overflow answerers. The response
rate from both groups was high considered other online survey in software
engineering that received approximately 14--20\%~\FIXME{double-check the
	citation again for the magic numbers.}~\citep{Punter2003}.

@@

The majority of users in both groups are experienced developers with more than
10 years of experience or between 5 to 10 years as depicted in
Figure~\ref{fig:survey_exp}. There are 59\% of the answerers in Group 1 that
have more than 10 years of software development experience, while a slightly
less percentage of 50\% in Group 2.

The participants are active users and regularly answer questions on Stack
Overflow (see Figure~\ref{fig:survey_answer_frequency}). Eighty-two (82\%) and
sixty (60\%) of answerers from Group 1 and Group 2  answer questions at least
once a week. More than half of the answerers very frequently (81--100\% of the
time) or frequently (61--80\% of the time) include code snippets in their
answers. To break down into two groups as depicted in
Figure~\ref{fig:survey_answer_frequency_with_code}, Group 1 very frequently
(48.7\%) and frequently (27.4\%) provide code examples when answering. Likewise,
Group 2 follow the same trend (very frequently for 32.1\% and frequently for
36.9\%). Interestingly, there is one participant who never includes code snippet
in his/her answer thus the results after this question is from 116 participants.

>>>>

\subsubsection{The visitor survey} 
The survey consists of 16 questions: 9 Likert's
scale questions, 3 yes/no questions, 2 multiple-choice questions, and 2
open-ended questions. The first four questions are mandatory while the other 12
questions will be shown to the participants based on their previous answers. The
survey collects information about the participant's software development
experience, the importance of Stack Overflow, reasons for reusing Stack Overflow
snippets, problems from Stack Overflow snippets, licensing of code on Stack
Overflow, and additional feedbacks. The survey was open for participation for 2 months, 
from 25 July 2017 to 25 September 2017, before we collected and analysed
the responses.

@@

\begin{table}
	\centering
	\caption{The Stack Overflow answerer taken the surveys}
	\label{tab:answerers}
	\begin{tabular}{lrrrr}
		\toprule
		Target group & Reputation & Sent emails & Answers & Rate \\
		\midrule
		Answerer Group 1 & 963,731--7,674 & 300 & 117 & 39\% \\
		Answerer Group 2 & 7,636--6,999 & 307 & 84 & 27\% \\
		\midrule
		Total & -- & 607 & 201 & 33\% \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\subsection{The answerer survey}
We received 117 answers (39\% response rate) from the first group and 84 answers
(27\% response rate) from the second group of Stack Overflow answerers. The response
rate from both groups was high considered other online survey in software
engineering that received approximately 14--20\%~\FIXME{double-check the
	citation again for the magic numbers.}~\citep{Punter2003}.

@@

The majority of users in both groups are experienced developers with more than
10 years of experience or between 5 to 10 years as depicted in
Figure~\ref{fig:survey_exp}. There are 59\% of the answerers in Group 1 
and 50\% of the answerers in Group 2 that
have more than 10 years of software development experience.

The participants are active users and regularly answer questions on Stack
Overflow (see Figure~\ref{fig:survey_answer_frequency}). Eighty-two (82\%) and
sixty (61\%) of answerers from Group 1 and Group 2  answer questions at least
once a week. More than half of the answerers very frequently (81--100\% of the
time) or frequently (61--80\% of the time) include code snippets in their
answers. To break down into two groups as depicted in
Figure~\ref{fig:survey_answer_frequency_with_code}, Group 1 very frequently
(48.7\%) and frequently (27.4\%) provide code examples when answering. Likewise,
Group 2 follow the same trend (very frequently for 32.1\% and frequently for
36.9\%). Interestingly, there is one participant who never includes code snippet
in his/her answer thus the results after this question is from 116 participants.
